Optimal (Multiway) Spatial Joins

### 2024-06-04 msj.tex
yufei

Finally, we construct $H^*$ by collecting the minimal segment (see definition in \eqref{eqn:hv:type2:H*}) of every segment $h' \in H'$ with $\minleft(h') \neq \infty$. This step takes $O(|H'|) = O(n)$ time.

>>>>

Finally, we construct $H^*$ by collecting the minimal segment (defined in \eqref{eqn:hv:type2:H*}) of every segment $h' \in H'$ with $\minleft(h') \neq \infty$. This step takes $O(|H'|) = O(n)$ time.
